Performance Models for Data Transfers: A Case Study with Molecular Chemistry Kernels

### 2019-04-12 ICPP-19/communications.tex
minor

	Given a schedule, \scomm($i$) and \scomp($i$) represent the
	start times of task $i$ on communication and computation
	resources. A schedule is feasible if for every time $t$, the
	amount of memory required by all tasks such that $\scomm(i) \leq t
	\leq \scomp(i) + COMP_i$ is not more than the memory capacity
	$C$. 
%%	\todo[inline]{SKumar: We do not need this assumption throughout the paper. CommVolume=CommTime is not true for experimental section. We used this assumption only in NP-hard proof for simplicity.}
%%	For simplicity, we assume in all of this paper that the
%%	amount of memory required by a task is proportional to its
%%	communication time, and without loss of generality we consider
%%	that memory size of a task is equal to its communication time.

 We assume through out the paper that communication time of a task is proportional to memory required by it, and follow conventional \textit{Comm Time = Latency + (Comm Volume)/Bandwidth} model.

	We call a task $i$ compute intensive if $COMP_i \ge COMM_i$, and
	communication intensive otherwise.

@@

%%		As \textit{Transfer time = Latency + (Data Volume)/Bandwidth}. 
		For simplicity, we consider input transfer time is same as input data volume (i.e., \textit{Latency = 0} and \textit{Bandwidth = 1}). Otherwise, we can adjust $C$ such that at any point in a schedule at max one $K_i$ and three $A_i$ tasks can be active.

@@

			We are grateful to Ajay Panyala for his help in installation of  NWChem on Cascade machine and providing internal details about the package and its inputs. This work was supported in part by the U.S. Department of Energy’s (DOE), Office of Science, Office of Advanced Scientific Computing Research, under awards 63823. Pacific Northwest National Laboratory is operated by Battelle for DOE under Contract DE-AC05-76RL01830.
		\end{acks}

>>>>

	Given a schedule, \scomm($i$) and \scomp($i$) represent the
	start times of task $i$ on communication and computation
	resources. A schedule is feasible if for every time $t$, the
	amount of memory required by all tasks such that $\scomm(i) \leq t
	\leq \scomp(i) + COMP_i$ is not more than the memory capacity
	$C$. 
%%	\todo[inline]{SKumar: We do not need this assumption throughout the paper. CommVolume=CommTime is not true for experimental section. We used this assumption only in NP-hard proof for simplicity.}
	For simplicity, we assume in all of this paper that the
	amount of memory required by a task is proportional to its
	communication time, and without loss of generality we consider
	that memory size of a task is equal to its communication volume.

%% We assume through out the paper that communication time of a task is proportional to memory required by it, and follow conventional \textit{Comm Time = Latency + (Comm Volume)/Bandwidth} model.
%%	
	We call a task $i$ compute intensive if $COMP_i \ge COMM_i$, and
	communication intensive otherwise.

@@

		As \textit{Transfer time = Latency + (Data Volume)/Bandwidth}. For simplicity, we consider input transfer time is same as input data volume (i.e., \textit{Latency = 0} and \textit{Bandwidth = 1}). Otherwise, we can adjust $C$ such that at any point in a schedule at max one $K_i$ and three $A_i$ tasks can be active.

@@

			We are grateful to Ajay Panyala for his help in installation of  NWChem on Cascade machine and providing internal details about the package and its inputs. This work was supported in part by the U.S. Department of Energy’s (DOE), Office of Science, Office of Advanced Scientific Computing Research, under award 63823. Pacific Northwest National Laboratory is operated by Battelle for DOE under Contract DE-AC05-76RL01830.
		\end{acks}
